---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# impactR.viz

<!-- badges: start -->
<!-- badges: end -->

`impactR.viz` proposes ready-to-go colors and color palettes for IMPACT, and a few functions for plats and maps.

## Installation

You can install the development version of impactR.viz from
[GitHub](https://github.com/) like so:

``` r
devtools::install_github("impact-initiatives-hppu/impactR.viz")
```

## Request

Please, do not hesitate to pull request any new viz, colors or color palettes, or to email request any change (gnoblet@zaclys.net).

## Colors 

Branding color palettes for REACH, AGORA and IMPACT are available. Functions to access colors and palettes are `color()` or `palette()`.

```{r example-colors, eval = TRUE}
library(impactR.viz)

# Get all saved REACH colors, named
color(unname = FALSE)[1:10]

# Extract a color palette as hexadecimal codes and reversed
palette(palette = "cat_5_ibm")

# Get all color palettes names
palette(show_palettes = T)[1:10]
```



## Charts

### Example 1: Bar chart

```{r, echo = FALSE, results = FALSE, message = FALSE}

# In order to add Segoe UI and Roboto Condensed
library(extrafont)
loadfonts()
```


```{r example-bar-chart, out.width = "65%", eval = TRUE}
library(impactR.viz)
library(palmerpenguins)
library(dplyr)
# install.packages("gghighlight")
# library(gghighlight)

df <- penguins |> 
  count(island) |> 
  mutate(freq = prop.table(n)*100) |> 
  arrange(freq)

# Simple bar chart
bar(df, "island", "freq", width = 0.5) 

# Vertical one, need some theme tweaking
bar(df, "island", "freq", width = 0.6, add_color = color("branding_agora_bordeaux"), flip = F, theme = theme_reach(axis_y = F, grid_major_x = F, axis_ticks_x = F)) 

df <- penguins |> 
  count(island, species, name = "count") |> 
  mutate(freq = count/sum(count)*100, .by = "island") 

# Simple bar chart by group with some alpha transparency
bar(df, "island", "freq", "species", title = "% of penguins by island and species",  add_text_expand_limit = 1.2, group_title = "Species") 

# Change of palette, change of theming to adapt
bar(df, "island", "freq", "species", group_title = "Species",  alpha = 0.6, flip = FALSE, title = "% of penguins by island and species", palette = "cat_3_tol_high_contrast", theme = theme_reach(axis_y = F, grid_major_x = F, axis_ticks_x = F))

# No palette = default to magma viridis
bar(df, "island", "freq", "species", group_title = "Species", width = 0.8, add_text_expand_limit = 1.2, title = "% of penguins by island and species", palette = NULL)
```

### Example 2: Point chart

At this stage, [point()] only supports categorical grouping colors with the `group` arg.

```{r example-point-chart, out.width = "65%", eval = TRUE}

# Simple point chart
point(penguins, "bill_length_mm", "flipper_length_mm", title = "What a good test title!")

# Point chart with grouping colors, different palette, greater dot size, some transparency, reversed color palette
point(penguins, "bill_length_mm", "flipper_length_mm", "island", palette= "cat_8_wong", group_title = "Islands", alpha = 0.7, size = 3)
```
